On the marginal value of swimming in woodland caribou

### 2021-05-25 paper/manuscript.Rmd
P4

We identified swimming events as two consecutive GPS locations (2-hour relocation rates) on different
islands. Newfoundland typically experiences pack ice in late winter and caribou may travel between
islands by walking over the ice. We restricted our dataset between April 1 and December 31 to
distinguish swimming from walking on ice. We calculated island residency as the duration of time,
measured on 2-hour relocation rates, an individual caribou was observed on an island. Residency was
therefore a proxy for when the benefits of foraging no longer exceeded the costs of swimming between
islands. Our test of the marginal value theorem for the case of oceanic swimming by caribou is based
on three assumptions: (1) resources are proportional to the size of each island; (2) caribou know
approximate value of the resources on an island before they swim to and from that island; and (3) the
cost of swimming to and from an island is less than the value of resources on that island when the
caribou departs. Should these assumptions hold, we would predict a positive relationship where caribou
depart smaller islands sooner than larger islands.

>>>>

We identified swimming events as two consecutive GPS locations (2-hour relocation rates) on different islands (n = 29, for collaring details see Peignier et al. 2019). Newfoundland typically experiences pack ice in late winter and caribou may travel between islands by walking over the ice. We restricted our dataset between April 1 and December 31 to distinguish swimming from walking on ice. We calculated island residency as the duration of time, measured on 2-hour relocation rates, an individual caribou was observed on an island. Residency was therefore a proxy for when the benefits of foraging no longer exceeded the costs of swimming between islands. Our test of the marginal value theorem for the case of oceanic swimming by caribou is based on three assumptions: (1) resources are proportional to the size of each island above approximately 0.1km2; (2) caribou know the approximate value of the resources on an island before they swim to and from that island; and (3) the cost of swimming to and from an island is less than the value of resources on that island when the caribou departs. Should these assumptions hold, we would predict a positive relationship where caribou depart smaller islands sooner than larger islands.
